|

### 2021-10-01 front-and-back-matter/99-appendices.Rmd
End of day:

@@

>>>>

### Calculating Gwet's AC1

Gwet's AC1 is defined as:

$$AC1 = \frac{observed\;agreement-chance\;agreement}{1-chance\;agreement}$$

In reference to a two-by-two table with cells A, B, C and D, it is calculated using the following:

\begin{equation}
  AC1 = \frac{\frac{A+D}{N}-e(\gamma)}{1-e(\gamma)}
  (\#eq:AC1-main)
\end{equation}

where $e(\gamma)$ is the chance agreement between raters, given as $2q(1-q)$, where

\begin{equation}
  q = \frac{(A+C)+(A+B)}{2N}
  (\#eq:AC1-supp)
\end{equation}

@@

<!-- TODO Need to include -->

### Forest plots for lipid fractions {#lipid-fraction-forest-plots}

<!-- TODO Need to add labels/captions to these -->

<!----------------------------------------------------------------------------->
```{r obsLipidsDementiaTC, echo = FALSE, results="asis", fig.pos = "H", out.width='100%'}
knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Dementia_TC_.png"))
```
<!----------------------------------------------------------------------------->

<!----------------------------------------------------------------------------->
```{r obsLipidsDementiaLDL, echo = FALSE, results="asis", fig.pos = "H", out.width='100%'}
knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Dementia_LDL_.png"))
```
<!----------------------------------------------------------------------------->

<!----------------------------------------------------------------------------->
```{r obsLipidsDementiaHDL, echo = FALSE, results="asis", fig.pos = "H", out.width='100%'}
knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Dementia_HDL_.png"))
```
<!----------------------------------------------------------------------------->

<!----------------------------------------------------------------------------->
```{r obsLipidsDementiaTG, echo = FALSE, results="asis", fig.pos = "H", out.width='100%'}
knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Dementia_TG_.png"))
```
<!----------------------------------------------------------------------------->
